Compositional equivalences based on Open pNets

### 2020-03-24 2016-Weak-FH-Bisim/WeakBisim.tex
more WI checked on page 72
Rabea, on a ici 2 "vrai contre exemples", les WI_564* et WI_6a

$ WI_{3a}(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{m1\_msg}\gets \texttt{m}, \texttt{m1\_ec}\gets n), \texttt{s2\_ec}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
$

@@

$ WI_6(n) = \openrule
         {\{\}, True, (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1+n)}
         {220 \OTWeakarrow {\tau} 100}
         \ \forall n\ge 0$

$ WI_{456}(n) = \openrule
         {\{\}, True, 
    (\texttt{s1\_msg}\gets \texttt{s1\_msg}, \texttt{s1\_ec}\gets \texttt{s1\_ec}+n)}
  {100 \OTWeakarrow {\tau} 100}
        $($\forall n\ge 0$)

$ WI_{564}(n) = \openrule
         {\{\}, True, 
    (\texttt{m1\_msg}\gets \texttt{m1\_msg}, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n, \texttt{m1\_ec}\gets \texttt{s2\_ec}+1+n)}
  {210 \OTWeakarrow {\tau} 210}
        $($\forall n\ge 0$)

$ WI_{645}(n) = \openrule
         {\{\}, True, 
    (\texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
  {220 \OTWeakarrow {\tau} 220}
        $($\forall n\ge 0$)

$ WI_6a(n) = \openrule
         {\{\}, True, 
         (\texttt{m1\_ec}\gets \texttt{s1\_ec}+1+n, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
         {220 \OTWeakarrow {\tau} 210}
         \ \forall n\ge 0$

@@

\medskip
$ WI_7(n) = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s1\_ec}+n)}
         {100 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 0$

$ 7' = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec}+n)}
         {210 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 0$

$ 7'' = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_ec}+n)}
         {220 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 1$

>>>>

$ WI_{3a}(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{m1\_msg}\gets \texttt{m}, \texttt{m1\_ec}\gets n, \texttt{s2\_ec}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
$

@@

$ WI_6(n) = \openrule
         {\{\}, True, (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1+n)}
         {220 \OTWeakarrow {\tau} 100}
         $

$ WI_{456*}(n) = \openrule
         {\{\}, True, 
    (\texttt{s1\_msg}\gets \texttt{s1\_msg}, \texttt{s1\_ec}\gets \texttt{s1\_ec}+n)}
  {100 \OTWeakarrow {\tau} 100}
        $

Note that the loop itself does not assign $s1\_msg$, but as we are in a self-loop of state 100, we can add the identity assignment on it.
\medskip

$ WI_{564*}(n) = \openrule
         {\{\}, True, 
    (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n, \texttt{m1\_ec}\gets \texttt{s2\_ec}+1+n)}
  {210 \OTWeakarrow {\tau} 210}
        $

$Post_{564}=\ post_{4}\shortotimes\ post_{6}\shortotimes\ post_{5}\\
= \left( (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})
\shortotimes (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1) \right)
\shortotimes () \\
= (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s2\_ec}+1, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1$

This result is INCORRECT: the Post cannot use $s1\_msg$, this variable is not available in state 210

$ WI_{645*}(n) = \openrule
         {\{\}, True, 
    (\texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
  {220 \OTWeakarrow {\tau} 220}
        $

$ WI_6a(n) = \openrule
         {\{\}, True, 
         (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s2\_ec}+1+n, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
         {220 \OTWeakarrow {\tau} 210}
         $

@@

\medskip
This result is INCORRECT: the Post cannot use $s1\_msg$, this variable is not available in state 220

The next two  transitions show the same problem, as they include dependencies on $s1\_msg$:

\medskip
$ WI_7(n) = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_ec}+n)}
         {100 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 0$

$ WI_{7a}(n) = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec}+n)}
         {210 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 0$

$ WI_{7b}(n) = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_ec}+n)}
         {220 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 1$
